Identifying covariate traits of trance and possession phenomena in the Ethnographic

### 2022-10-20 Readme.Rmd
some edits

```{r }
trance = sccs %>% 
  filter(var_id == 'EA112') %>% 
  count(var_name,code,var_description) %>% 
  rename(name = var_name, description = var_description, count = n)

trance %>% 
  select(-code) %>% 
  add_row(name = 'Total', description = '', count = 151) %>% 
  kable('simple')
```

@@

```{r }
trance %>% 
  mutate(
    possession_trance = case_when(
      code %in% c(3,4,6,7) ~ 'possession trance',
      code %in% c(1,2,8,5) ~ 'other'
    ) %>% 
      fct_relevel('possession trance')
  ) %>% 
  group_by(possession_trance) %>% 
  summarise(count = sum(count)) %>% 
  kable('simple')
```

>>>>

```{r }
trance = sccs %>% 
  filter(var_id == 'EA112') %>% 
  count(var_name,code,var_description) %>% 
  rename(name = var_name, description = var_description, count = n) %>% 
  mutate(
    possession_trance = case_when(
      code %in% c(3,4,6,7) ~ 'possession trance',
      code %in% c(1,2,8,5) ~ 'other'
    ) %>% 
      fct_relevel('possession trance')
  )

trance %>% 
  select(description,code,name,possession_trance,count) %>%
  rename(outcome = possession_trance) %>% 
  add_row(name = 'Total', description = '', count = 151) %>% 
  kable('simple')
```

@@

```{r }
trance %>% 
  group_by(possession_trance) %>% 
  summarise(count = sum(count)) %>% 
  kable('simple')
```
